Software Ticket Quality

### 2017-10-15 proposal/mprop.tex
Added the second paper

Secret Life of Bugs (\citep{aranda2009secret}):
\begin{itemize}
\item What were the goals?
  The paper tries to understand and analyze common bug fixing coordination
  activities. Another goal of the paper was to analyze the reliability of
  repositories in terms of software projects coordination and propose
  different directions on how to implement proper tools.
\item What was the method?
  They executed a field study which was split into two parts:
  \begin{itemize}
  \item firstly, they did an exploratory case study of bug repos histories;
  \item secondly, they conducted a survey with professionals (i.e.\ testers,
    developers).
  \end{itemize}
  All data and interviews were conducted using Microsoft bug repositories and
  employees.
\item What did they learn?
  They learned that there are multiple factors which influence the coordination
  activities that revolve around bug fixing, such as organizational, social and
  technical knowledge, thus one cannot infer any conclusions only by automatic
  analysis of the bug repositories. Also, through surverying the professionals,
  they reached the conclusion that there are 8 main goals which can be used for
  better tools and practices:
  \begin{itemize}
  \item probing for ownership;
  \item summit;
  \item probing for expertise;
  \item code review;
  \item triaging;
  \item rapid-fire emailing;
  \item infrequent, direct email;
  \item shotgun emails.
  \end{itemize}

\item Link to other work
  \begin{itemize}
    \item @inproceedings{anvik2006should,
  title={Who should fix this bug?},
  author={Anvik, John and Hiew, Lyndon and Murphy, Gail C},
  booktitle={Proceedings of the 28th international conference on Software engineering},
  pages={361--370},
  year={2006},
  organization={ACM}
    }
      \item @inproceedings{bettenburg2008makes,
  title={What makes a good bug report?},
  author={Bettenburg, Nicolas and Just, Sascha and Schr{\"o}ter, Adrian and Weiss, Cathrin and Premraj, Rahul and Zimmermann, Thomas},
  booktitle={Proceedings of the 16th ACM SIGSOFT International Symposium on Foundations of software engineering},
  pages={308--318},
  year={2008},
  organization={ACM}
      }
        \item @inproceedings{ko2007information,
  title={Information needs in collocated software development teams},
  author={Ko, Andrew J and DeLine, Robert and Venolia, Gina},
  booktitle={Software Engineering, 2007. ICSE 2007. 29th International Conference on},
  pages={344--353},
  year={2007},
  organization={IEEE}
        }
  \end{itemize}
\item Relevance to our work: this paper is one of the key papers for our
  research paper.
\end{itemize}

\citep{Korkala2014WasteIdentification}
\begin{itemize}
\item What were the goals?

\item What was the method?
\item What did they learn?
\item Link to other work
\item Relevance to our work
\end{itemize}

>>>>

Secret Life of Bugs (\citep{aranda2009secret}):
\begin{itemize}
\item What were the goals?
  The paper tries to understand and analyze common bug fixing coordination
  activities. Another goal of the paper was to analyze the reliability of
  repositories in terms of software projects coordination and propose
  different directions on how to implement proper tools.
\item What was the method?
  They executed a field study which was split into two parts:
  \begin{itemize}
  \item firstly, they did an exploratory case study of bug repos histories;
  \item secondly, they conducted a survey with professionals (i.e.\ testers,
    developers).
  \end{itemize}
  All data and interviews were conducted using Microsoft bug repositories and
  employees.
\item What did they learn?
  They learned that there are multiple factors which influence the coordination
  activities that revolve around bug fixing, such as organizational, social and
  technical knowledge, thus one cannot infer any conclusions only by automatic
  analysis of the bug repositories. Also, through surverying the professionals,
  they reached the conclusion that there are 8 main goals which can be used for
  better tools and practices:
  \begin{itemize}
  \item probing for ownership;
  \item summit;
  \item probing for expertise;
  \item code review;
  \item triaging;
  \item rapid-fire emailing;
  \item infrequent, direct email;
  \item shotgun emails.
  \end{itemize}
\item Relevance to our work: this paper is one of the key papers for our
  research paper.
\end{itemize}

\citep{bettenburg2008makes}
\begin{itemize}
\item What were the goals?
  The main goal of the paper was to investigate the \textbf{quality of bug reports} from a developer's
  point of view, based on the typical information found in such a report (e.g. stack traces, screenshots).
\item What was the method?
  The authors conducted a massive survey with over 450 respondents. The survey was online and it targeted
  developers from Mozilla, Apache and Eclipse.
\item What did they learn?
  The main conclusion of this research paper was that well written bug reports will more likely get the 
  attention of the developers. Thus, including steps to reproduce the bugs or stack traces proved to increase
  the quality of the bug report. Also, an important achievement reached by the authors was the development of
  a prototype tool called Cuezilla that could estimate, with an accuracy rate of 31\-48\%, the quality of a bug
  report.
\item Relevance to our work: it is relevant to our research in that it provides valuable insight into 
  what makes for a good bug report based on actual professionals' opinions.
\end{itemize}
